
Question 2.c
The tukey ladder model said that once we calculate the correlation and if the value of the power is negitive, we have to transform with 1/datacolumn . 
```{r}
data(pressure)
attach(pressure)
x=pressure$temperature
y=pressure$pressure
x = x+273.15
y = y*0.133
NewTransforedTemperature = 1/(x)
CleanedNewPowerddata = data.frame(x,NewTransforedTemperature)
CleanedNewPowerddata
plot(CleanedNewPowerddata$x~CleanedNewPowerddata$NewTransforedTemperature, main = "The pressure data scatter plot" )
fit = lm(CleanedNewPowerddata$x~CleanedNewPowerddata$NewTransforedTemperature) 
abline(fit, lty=4, col='orange')

```
The 1/x calculation brings a lot of straigtness. It looks very much transformed now.

Question 2 : d
For the above graph i have drawn, the intercept is to be calculated.
```{r}
x = pressure$temperature
y=pressure$pressure
x = x+273.15
y = y*0.133
NewTransforedTemperature = 1/(x)
CleanedNewPowerddata = data.frame(x,NewTransforedTemperature)
CleanedNewPowerddata
plot(CleanedNewPowerddata$x~CleanedNewPowerddata$NewTransforedTemperature, main = "The pressure data scatter plot" )
fit = lm(CleanedNewPowerddata$x~CleanedNewPowerddata$NewTransforedTemperature) 
abline(fit, lty=4, col='orange')

CorrelationValuforNewdata = cor(CleanedNewPowerddata,use = "everything", method = c("pearson"))
corlation= CorrelationValuforNewdata
corlation
```
The correlation between x and y tells that a value of 0.97 , which says that we can use a power factor of 0.97.
but these can be again done in the other way explained in the book. lower, upper and mid summariess, get p as a set of medians obtained for the summaries. usse tha p for the calculations.

Box Cox Tranformations
```{r}
library(MASS)
boxcox(CleanedNewPowerddata$x~CleanedNewPowerddata$NewTransforedTemperature)
plot(log(CleanedNewPowerddata$x)~CleanedNewPowerddata$NewTransforedTemperature, ylab = "Log(PressureOfData)", xlab = "Inverse temperature", col = "orange")
fit = lm(log(CleanedNewPowerddata$x)~CleanedNewPowerddata$NewTransforedTemperature)
print(fit)
```


